Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-04-18 paper/ms.tex
manuscript with cosmic variance plots
new caption in last figure

\begin{figure}
\includegraphics[width=0.46\textwidth, height=0.33\textwidth]{mmin_dfocc1.png}
\caption{Width of the halo number distribution over the 54 mock field of the simulation ($\Delta \log \left( N_{\mathrm halos}/\tilde{N}_{\mathrm halos}\right)$) of the central 68 (blue diamonds) and  95(red circles)  percentiles vs $M_{\rm min}$. Points are color coded according to their associated value of $\Delta M \equiv M_{\rm min}-M_{\rm min}$. The green line diagonal line accounts for the 1:1 relation and the green vertical lines represent  the 16, 50 and 84 percentiles  of the posterior probability distribution of \mmin.}
\label{fig:cosmicv}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.49\textwidth]{fig6.pdf}
\caption{$1\sigma$ width of the number density distribution over the
  54 mock fields of the simulation as a function of \mmin. 
  Only the models that have a good match with observations
  ($\chi_{\mathcal M}/2 < 1$) are included.
  The strong dependence of $n/ \langle n\rangle$ with \mmin was
  parameterized as a power law with the parameters shown in the legend.
\label{fig:cosmicv}}
\end{figure}
